### 2017-07-24 src/4_OnlineLearning.tex
avance correcciones cap 3

\noindent where $\mathcal{H}$ is called the {\em hypothesis space}, is the space of functions that the algorithm is allowed to search. The selection of $f$ is based on the minimization of the expected error of the loss function $V(f(x),y)$ defined as:

\begin{eqnarray*}
 V(f(\cdot),\cdot): X\times Y &\rightarrow & Y \\
  (x, y) &\rightarrow &V(f(x),y)
\end{eqnarray*}

\noindent $V(f(x),y)$ denote the price paid for mistakes. Therefore, $V(f(x),y)=0$ if $f(x)=y$.

@@

\begin{equation}
\label{eq:expetedrisk}
E[V(f(\cdot),\cdot)] = \int_{X\times Y} V(f(x),y)\;dp(x,y)\,,
\end{equation}

@@

@@

The ERM is a Riemann sum approximation of the expected error of $f$ shown in equation \ref{eq:expetedrisk}, where $dp(x,y) \approx 1/n$.

>>>>

\noindent where $\mathcal{H}$ is called the {\em hypothesis space}, i.e. the space
of functions that the algorithm is allowed to search. The selection of
$f$ is based on the minimization of the expected error of the loss
function $V(f(x),y): Y \times Y$ defined as:

\begin{eqnarray*}
 V & \rightarrow & \mathbb{R}^+ \\
  (f(x), y) &\rightarrow & V(f(x),y)
\end{eqnarray*}

\noindent where $V(f(x),y)$ denote the price paid for mistakes, $f:X=\R^m\to Y$ and
$y=f(x)\in\R$. Therefore, $V(f(x),y)=0$ if $f(x)=y$.

@@

\begin{equation}
\label{eq:expetedrisk}
E[V(f(x),y)] = \int_{X\times Y} V(f(x),y)\;dp(x,y)\,,
\end{equation}

@@

\begin{equation*}
\hat{f} = \argmin_{f \in \mathcal{H}} R_{\text{emp}}[f] 
\end{equation*}

\noindent where,

@@

The ERM is a Riemann sum approximation of the expected error of $f$ shown in
equation \ref{eq:expetedrisk}. By the law of large numbers it is known that:

\begin{equation}
\frac{1}{n} \sum_{i=1}^n V(f(x_i),y_i) \xrightarrow{n \rightarrow \infty}  E[V(f(x),y)]
\end{equation}
